Aligning marine species range data to better serve science and conservation

### 2016-03-01 ms_6_supplemental.Rmd

## Info on data prep

### processing AquaMaps

* start with .sql files - three of 'em - how to get 'em?
* turn into .csvs, which columns are critical for this analysis? simplify

### downloading and processing IUCN maps

### creating master species list for co-listed species

* using AquaMaps and IUCN, and IUCN master list, create the big list
* which columns are included?
* adjust this master list to use IUCN SID only for parent - eliminate the whole question of parent/subpop? for the purpose of this analysis

## descriptions of IUCN and AM data sets

@@

 As of December 2015, AquaMaps current native distribution maps have been produced for `r nrow(spp_am)` species.

 ___Move to supplementary materials. - BH___: For example, as of this writing, IUCN has released no spatial data for class Elasmobranchii (cartilaginous fishes including sharks and rays); and while IUCN offers a large number of maps within class Actinopterygii (ray-finned bony fishes), the available maps include only a few primarily tropical taxonomic sub-groups, such as wrasses, damselfish, butterflyfish, tunas, and billfishes, but are missing economically important subgroups including salmon, rockfish, and clupeids.  However, IUCN's criterion of comprehensive assessment greatly reduces the risk of sample bias within the bounds of the assessed taxonomic groups.

>>>>

#Outline

## Data processing

All code is publicly available and freely downloadable [here on GitHub](link to github).

### AquaMaps

AquaMaps data was provided by AquaMaps directly via ftp. Three SQL files were sent that contained (1) list of all `r nrow(spp_am)` species and their taxonomic information, (2) information for all (292,000?) half degree cells used for range mapping and (3) the probability of occurrence per cell for all `r nrow(spp_am)` species. These were extracted into .csv form using R Statistical Software.

#### Possible figures
- Map of all cells
- Map of # of species per cell
- Example aquamaps (one species range)

### IUCN

@@

JA: I think here we only need a few sentences describing how we downloaded the data and on what date. Link to the IUCN spatial data website.

IUCN data is provided as polygon shapefiles. These vectors were rasterized to the same cell resolution as AquaMaps data (0.5 degrees).

#### Possible figures

#### Caveats
For example, as of this writing, IUCN has released no spatial data for class Elasmobranchii (cartilaginous fishes including sharks and rays); and while IUCN offers a large number of maps within class Actinopterygii (ray-finned bony fishes), the available maps include only a few primarily tropical taxonomic sub-groups, such as wrasses, damselfish, butterflyfish, tunas, and billfishes, but are missing economically important subgroups including salmon, rockfish, and clupeids.  However, IUCN's criterion of comprehensive assessment greatly reduces the risk of sample bias within the bounds of the assessed taxonomic groups.
